Fully structured proof theory for intuitionistic modal logics

### 2020-07-01 BicolorNS/aiml20/aiml20.tex
working on the final version: answering review 1

\section{Introduction}

Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.

@@

Similarly, proof systems have been designed for intuitionistic modal logic both as labelled sequent systems~\cite{simpson1994} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara}.
%
Surprisingly, in both settings, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.

>>>>

\section{Introduction}
\marianela{I added in the first paragraph the labelled natural deduction with three cites referencing the classical case. I did that so then in the third paragraph I added the reference of Galmiche and Sahli.}
%Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.

Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction~\cite{fitting1983,prawitz1965,siemens1977} and labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.

@@

Similarly, proof systems have been designed for intuitionistic modal logic as labelled sequent systems~\cite{simpson1994}, labelled natural deduction systems~\cite{galmiche2010} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara}.
%
Surprisingly, in nested and labelled sequents, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.

\marianela{If we want to make an specific distinction between our system and Galmiche/Sahli system I would say:

	In \cite{galmiche2010}, Galmiche and Salhi present label-free natural deduction systems
	for the different intuitionistic modal logics that are not using the \rn d-axiom. In this article, we present a labelled sequent calculus and a nested sequent calculus. We consider that sequent calculus is much better	suited for automated proof search than natural deduction.}
%
